Large-Scale Marine Protected Areas in the World's Largest Tuna Fishery

### 2019-04-22 docs/old_ms/PIPA_Palau030319.tex
Added new version from John

ENSO events are known to drive the behavior of fishing vessels, especially in PNA waters, which may drive reallocation of fishing effort \cite{lehodey_1997,kroodsma_2018,aqorau_2018}. We do our best control for these environmental changes by incorporating the NINO4 anomaly index in our analyses, and by tracking non-displaced vessels as a group that is equally affected by the environmental variation. For example, we observe that both displaced and non-displaced vessels shifted their effort to the Western margin of the PNA region, namely Kiribati's Gilbert Islands and Tuvalu. However, displaced vessels redistribute a greater proportion of fishing effort to these areas, as well as the High Seas (Fig \ref{fig:fishing_raster_diff}). Our analysis shows that sea surface temperature variation does have an effect on our crowding and behaviroal methods, but that by itself does not explain the observed patterns. While environmental variation certainly influences behavior, policy and management interventions such as moratorium and spatial closures can have an equally big effects \cite{kroodsma_2018}.

@@

Our work suggests that the implementation of a Large-Scale Marine Protected Areaa had little impact on total fishing effort, but that it may result in revenue losses. The closure caused a crowding effect, which causes some vessels to redistribute to areas close by. The Parties to the Nauru Agreement have shown that multinational cooperation in management of transboundary resources can have management and economic benefits \cite{lehodey_1997,aqorau_2018}. Overlaying conservation interventions over existing management schemes must be accompained by similar dialogues and international cooperation, so that the benefits of conservation are captured by those incurring the costs. Furthermore implementation of Large-Scale Marine Protected Areas must be accompanied by traditional fisheries management to maximize effectivenes, consider the opportunity costs of such closures \cite{smith_2010}, and identify sustainable financing mechanisms\cite{mallin_2019} that would compensate losses and incentivize marine conservation in the long term.

>>>>

ENSO events are known to drive the location of fish and behavior of fishing vessels, especially in PNA waters \cite{lehodey_1997,kroodsma_2018,aqorau_2018}. We do our best control for these environmental changes by incorporating the NINO4 anomaly index in our analyses, and by tracking non-displaced vessels as a group that is equally affected by the environmental variation. For example, we observe that both displaced and non-displaced vessels shifted their effort to the Western margin of the PNA region, namely Kiribati's Gilbert Islands and Tuvalu. However, displaced vessels redistribute a greater proportion of fishing effort to these areas, as well as the High Seas (Fig \ref{fig:fishing_raster_diff}). Our analysis shows that sea surface temperature variation does have an effect on our crowding and behaviroal methods, but that by itself does not explain the observed patterns. While environmental variation certainly influences behavior, policy and management interventions such as moratorium and spatial closures can have an equally big effects \cite{kroodsma_2018}.

@@

Our work suggests that the implementation of a Large-Scale Marine Protected Areaa had little impact on total fishing effort, but that it may result in revenue losses. The closure caused a crowding effect, which causes some vessels to redistribute to areas close by. The Parties to the Nauru Agreement have shown that multinational cooperation in management of transboundary resources can have management and economic benefits \cite{lhavice_2013,aqorau_2018}. Overlaying conservation interventions over existing management schemes must be accompained by similar dialogues and international cooperation, so that the benefits of conservation are captured by those incurring the costs. Furthermore implementation of Large-Scale Marine Protected Areas must be accompanied by traditional fisheries management to maximize effectivenes, consider the opportunity costs of such closures \cite{smith_2010}, and identify sustainable financing mechanisms\cite{mallin_2019} that would compensate losses and incentivize marine conservation in the long term.
